Machine Learning based TIR predictor - Methods

### 2020-05-14 main.tex
Reconstruction and writing (from Maciej)
Updated 14/05/20
Updated Results 140520

\title{Machine Learning based TIR predictor}
\author{u6015325 }
\date{\today{}}

@@

>>>>

\topmargin -.5in
\textheight 9in
\oddsidemargin -.25in
\evensidemargin -.25in
\textwidth 7in

\title{Machine Learning based TIR predictor}
\author{}
\date{\today{}}

@@

\subsection{Sequence embedding}
First problem to be tackled was how to embed the sequence to give features (sequences) a numerical form. As we will be using a Gaussian Process for regression we have investigated use of different types of kernels for embedding \cite{Ben-Hur2008}. We compared performance of Dot Product, RBS and a number of string kernels: spectrum, mixed spectrum, weighted degree and weighted degree with shifting \textcolor{red}{Figure X}. Since we found that the spectrum kernel performed the best, we have used it in subsequent studies. More specifically, we used a summary of three kernels: spectrum kernel to process the core 6bp and dot product kernel to process the 7bp flanking sequences both upstream and downstream of the core sequence. 
\\
\\
\textcolor{red}{Do we need a figure showing comparison of different kernel's performance? I think it would be useful}

\subsection{Initial predictions}

\subsection{Second and subsequent rounds predictions}

### 2020-05-14 methods.tex
Updated Results 140520

\begin{itemize}
    \item \textit{Gaussian process regression (GPR)}. Gaussian Process regression model, which predicts the label (TIR) and how uncertain we are about our prediction (confidence width); Since the sequences in provided data have the pattern that the core area is different from each other, and other areas are similar. So the kernel for Gaussian Process we are using is the sum of kernels, for core areas we use spectrum kernel with string as input directly, and for other areas we use one-hot encoding and dot product kernel for simplicity.
    \item \textit{Upper confidence bound (UCB)}. recommends sequences to test for next round.
\end{itemize}

@@

\textbf{Choice of kernel function:} \textit{Spectrum kernel.}

>>>>

To automatically design the RBS sequences in batch using machine learning, we need to consider two parts: 
1) Design an regression algorithm which takes the RBS sequences as input and returns the predicted TIR scores and the confidence interval for the prediction. 
2) Design an online learning approach which recommends the RBS sequences based on the predicted TIR scores and confidence interval. 
Such online learning approach provides the $\textit{exploitation-exploration balance}$. 
We show the corresponding methods we use in the below.

We consider our experimental design problem as the problem of sequentially optimising an unknown reward function $f: \mathcal{D} \rightarrow \mathbb{R}$, where $\mathcal{D}$ is the set containing all RBS sequence point, and $f(\mathbf{x})$ is the TIR score at $\mathbf{x}$. 
In each round $t$, we choose a set of $m$ points $\mathcal{S}_t \subset \mathcal{D}$ and observe the function values of each points in the selected set $\mathcal{S}_t$, i.e. $y_i = f(\mathbf{x}_i) + \epsilon_i$, for all $i \in \mathcal{S}$, where $\epsilon_i$ is the noise (we assume the noise is under Gaussian distribution with some unknown mean and variance). 
The noise influenced by the accuracy RBS calculator and other experimental interference (e.g. \textcolor{red}{To be added}). 
Our goal is to pick RBS sequence with the largest possible TIR score after the total number of rounds $N$.

\begin{itemize}
    \item \textit{Gaussian process regression (GPR)}. We model $f$ as a sample from a \textit{Gaussian process} $GP(\mu(\mathbf{x}), k(\mathbf{x}, \mathbf{x'}))$, which is specified by the mean function $\mu(\mathbf{x})=\mathbb{E}[f(\mathbf{x})]$ and the kernel (or covariance) function $k\left(\mathbf{x}, \mathbf{x}^{\prime}\right)=\mathbb{E}[(f(\mathbf{x})-\left.\mu(\mathbf{x}))\left(f\left(\mathbf{x}^{\prime}\right)-\mu\left(\mathbf{x}^{\prime}\right)\right)\right]$. We will introduce the kernel function we choose in the below. 
    A Gaussian process regression model \cite{Rasmussen2004},

    \item \textit{Upper confidence bound (UCB)}. recommends sequences to test for next round.
\end{itemize}

@@

\textbf{Choice of kernel function:} \textit{Spectrum kernel.} Since the sequences in provided data have the pattern that the core area is different from each other, and other areas are similar. So the kernel for Gaussian Process we are using is the sum of kernels, for core areas we use spectrum kernel with string as input directly, and for other areas we use one-hot encoding and dot product kernel for simplicity.
